---
title: "Homework 1"
author: "Xuan Lu"
date: "2023-09-18"
output: 
  html_document: 
    toc: true #table of contents = true
    toc_float: true #floating table of contents on the side
---
# Question 0.1

```{r github_repository}

usethis::use_git_config(
    user.name = "Xuan Lu", 
    user.email = "xuan.lu.080229@gmail.com"
  )

```


# Question 1

First let's load the dataset and take a look at what variables are contained in the dataset.

```{r library_packages, message = FALSE}
library(moderndive)
library(tidyverse)
```


```{r load_dataset}

data("early_january_weather")
head(early_january_weather)

```

The dataset has `r nrow(early_january_weather)` observations and `r ncol(early_january_weather)` variables.
The mean of variable "temperature" is `r mean(early_january_weather$temp)`. 

Using temperature as dependent variable (Y) and time_hour as independent variable (X), the dataset can be presented in the following scatterplot: 

```{r create_scatterplot}

library(tibble)
library(ggplot2)
ggplot(early_january_weather, 
       aes(x = time_hour, 
           y = temp, colour = humid
          )
       ) + geom_point()

```

Based on the graph, it seems like temperature fluctuates frequently as time_hour increases, but overall there seems to be an increasing trend. As time_hour and temperature increases, it seems like humidity also increases.

Next, I am saving the plot to my project directory using ggsave.

```{r save_scatterplot}

ggsave( filename = "scatter_time_temp", plot = last_plot(), 
        device = "png", 
        path = NULL, 
        scale = 1, 
        width = NA, 
        height = NA, 
        units = c("in", "cm", "mm", "px")
      )

```

# Question 2

Create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r create_dataframe}

df_question2 = 
  tibble(
    samp = rnorm(10),
    log_vec = samp > 0,
    cha_vec = c("I", "don't", "know", "how", "to", "name", "entries", "in", "this", "vector"),
    fac_vec = factor(c("yes","no","unknown","yes","yes","no","no","no","yes","yes"))
  )
head(df_question2)

```

* The mean of variable samp is `r mean(pull(df_question2, samp))`.
* The mean of variable log_vec is `r mean(pull(df_question2, log_vec))`.
* The mean of variable cha_vec is `r mean(pull(df_question2, cha_vec))`.
* The mean of variable fac_vec is `r mean(pull(df_question2, fac_vec))`.

Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). 

```{r, message = FALSE, results = FALSE, warning = FALSE}

as.numeric(
  pull(
    df_question2, log_vec)
  )
as.numeric(
  pull(
    df_question2, cha_vec)
  )
as.numeric(
  pull(
    df_question2, fac_vec)
  )

```

Warning messages for cha_vec and fac_vec are generated, stating that arguments are not numeric or logical, and returning `NA`. This is because factors and characters are not numbers, and cannot be converted to numeric variables. This helps explain why the mean for `cha_vec` and `fac_vec` are NAs. 
