---
title: "Homework 1"
author: "Xuan Lu"
date: "2023-09-18"
output: 
  html_document: 
    toc: true #table of contents = true
    toc_float: true #floating table of contents on the side
---
# Question 0.1

```{r}
usethis::use_git_config(
    user.name = "Xuan Lu", 
    user.email = "xuan.lu.080229@gmail.com"
  )
```


# Question 1

First let's load the dataset and take a look at what variables are contained in the dataset.
```{r load_dataset}
library(moderndive)
data("early_january_weather")
head(early_january_weather)
```

The dataset has `nrow(early_january_weather)` observations and `ncol(early_january_weather)` variables.
The mean of variable "temperature" is `mean(early_january_weather$temp)`. 

Using temperature as dependent variable (Y) and time_hour as independent variable (X), the dataset can be presented in the following scatterplot: 

```{r create_scatterplot}
library(tibble)
library(ggplot2)
scatter_time_temp <- ggplot(early_january_weather, 
                            aes(x = time_hour, 
                                y = temp, 
                                colour = humid
                              )) + geom_point()
```


Based on the graph, it seems like temperature fluctuates frequently as time_hour increases, but overall there seems to be an increasing trend. As time_hour and temperature increases, it seems like humidity also increases.
Export your scatterplot to your project directory using ggsave.

```{r save_scatterplot}
ggsave( filename = "scatter_time_temp", plot = last_plot(), 
        device = "png", 
        path = NULL, 
        scale = 1, 
        width = NA, 
        height = NA, 
        units = c("in", "cm", "mm", "px")
      )
```

# Question 2

Create a data frame comprised of:

a random sample of size 10 from a standard Normal distribution
a logical vector indicating whether elements of the sample are greater than 0
a character vector of length 10
a factor vector of length 10, with 3 different factor “levels”
Try to take the mean of each variable in your dataframe. What works and what doesn’t?

```{r}

```

